COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario

### 2021-02-26 outputs/paper/paper.Rmd
Change title

```{r q15, fig.align='center', fig.cap="How much loans have you applied for the COVID-19 related reasons?", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Grant value")+
  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()

>>>>

```{r q15, fig.align='center', fig.cap="Loan amount applied", fig.width=8, fig.height=4, echo= FALSE, message=FALSE, warning=FALSE}
data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Grant value")+
  ggtitle("Loan amount applied for COVID-19 related reasons")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()
